---
title: "Data cleaning and preparation for Kantar Public Attitude Tracker 2022 data"
author: "K L Purves"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  html_document:
    
    keep_md: true # save images
    self_contained: true
    code_folding: hide
    df_print: paged
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean
html_notebook:
  theme: cerulean
toc: yes
editor_options: 
  chunk_output_type: inline
---


# set up

## Environment
```{r, include=FALSE}
# clear global environment
remove(list = ls())
```


```{r setup, warning=FALSE,echo=FALSE}

# source in all functions in the function library folder
files.sources = paste0("./functions/",list.files("./functions"))
sapply(files.sources, source)

knitr::opts_chunk$set(echo = TRUE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE,
                      fig.width = 15,
                      fig.asp = 1,
                      out.width = "100%")


# this chunk installs any required packages if you dont already have them in your local library. 
# List of required package names

packages <- c("ggplot2","gtsummary","kableExtra", 
              "readr",
              "readxl","psych",
              "haven", "expss",
              "summarytools","stringr",
              "nnet","broom",
              "purrr", "skimr",
              "dplyr", "tidyr")

# apply function to install and load functions as needed. Prints version to screen.
# see function library for code (../functions)
load_packages(packages)



```

Set up ggplot theme for the plots

```{r ggplot theme}

theme_personal <-  function(){theme(
    text = element_text(color = "black"),
    title = element_text(size = 12),
    axis.title = element_text(color = "black",
                              size = 10),
    axis.text = element_text(color = "black",
                             size=9),
    axis.text.x = element_text(angle = 45,
                               hjust=1),
    axis.title.y = element_blank(), 
    axis.line = element_line(colour = "black", 
                      size = 1, linetype = "solid"),
    legend.background = element_blank(),
    legend.box.background = element_blank(),
    panel.background = element_blank(), 
    panel.grid.minor.y = element_line(
      colour = "gray",
      linetype = "dashed",
      size = 0.1
      ),
    panel.grid.major.y = element_line(
      colour = "gray",
      linetype = "dashed",
      size = 0.2
      ),
    axis.ticks = element_blank()
    )}

```
# read in raw data

```{r read in raw data}
#import data
df <- read_sav("/Users/kirstinpurves/Library/CloudStorage/OneDrive-SharedLibraries-OurFutureHealth/Main Share - Documents/Our Future Health - Project Team/Behavioural Science/Public attitudes survey 2021/Raw data DO NOT EDIT/262323129-40C_Our Future Health_Dataset_FINAL.sav")
```

skim the data for missingness, completeness and unique values

```{r quick view of file structure and contents, warning=FALSE}

skim(df)

```

Turn character variables into factors using labels instead of values. Use is.labelled function from custom function library

```{r convert to labelled factor}

factor_df <- df %>%
  mutate_if(is.labelled,as_factor)
          
```

Skim new factor labelled data. We can use this for anything where labels are useful. Retain original df for dummy coding.

```{r skim factor df}

skim(factor_df)
```

# Data cleaning

Aligned with Alice's approach. Create the same variables and recode in the same way she did in the preliminary analyses so I can extend these.

## create new  variables dichotomousing or collapsing groups

Would take part in our future health (**OFHACT**)

*dichotomous (Yes, no + unsure)*
**ofhact_agree**

*three groups (Yes, No, Unsure)*
**ofhact_all**

*unsure vs no*
**ofhact_unsure**


Would want genetic feedback for preventable or treatable condition (**GENFBACK_1**)

*dichotomous (yes, no + unsure)*
**GENFBACK_prevent_agree**


*three groups (yes, no, unsure)*
**GENFBACK_prevent_all**

Would want genetic feedback for NOT preventable or treatable condition (**GENFBACK_2**)

*dichotomous (yes, no + unsure*
**GENFBACK_no_prevent_agree**


*three groups (Yes, no, unsure)*
**GENFBACK_no_prevent_all**

Would want genetic feedback for ancestry (**GENFBACK_3**)

*dichotomous (yes, no + unsure*
**GENFBACK_ancestry_agree**


*three groups (Yes, no, unsure)*
**GENFBACK_ancestry_all**


```{r create new variables}

factor_df <- factor_df %>%
  mutate(ofhact_agree = 
         as.factor(case_when(OFHACT == "Yes definitely" ~ "Yes", 
         OFHACT == "Yes probably" ~ "Yes",
         OFHACT == "No, probably not" ~ "No",
         OFHACT == "No, definitely not" ~ "No",
         OFHACT == "Not sure / it depends" ~ "No")),
         
         ofhact_all = 
         as.factor(case_when(OFHACT == "Yes definitely" ~ "Yes", 
         OFHACT == "Yes probably" ~ "Yes",
         OFHACT == "No, probably not" ~ "No",
         OFHACT == "No, definitely not" ~ "No",
         OFHACT == "Not sure / it depends" ~ "Unsure")),
         
         ofhact_unsure = 
         as.factor(case_when(OFHACT == "Yes, definitely" ~ NA_character_, 
         OFHACT == "Yes, probably" ~ NA_character_,
         OFHACT == "No, probably not" ~ "No",
         OFHACT == "No, definitely not" ~ "No",
         OFHACT == "Not sure / it depends" ~ "Unsure")),
         
         GENFBACK_prevent_agree = 
         as.factor(case_when(GENFBACK_1 == "Yes, definitely" ~ "Yes", 
         GENFBACK_1 == "Yes, probably" ~ "Yes",
         GENFBACK_1 == "No, probably not" ~ "No",
         GENFBACK_1 == "No, definitely not" ~ "No",
         GENFBACK_1 == "Not sure / it depends" ~ "No",
         GENFBACK_1 == "Prefer not to say" ~ "No")),
         
         GENFBACK_prevent_all = 
         as.factor(case_when(GENFBACK_1 == "Yes, definitely" ~ "Yes", 
         GENFBACK_1 == "Yes, probably" ~ "Yes",
         GENFBACK_1 == "No, probably not" ~ "No",
         GENFBACK_1 == "No, definitely not" ~ "No",
         GENFBACK_1 == "Not sure / it depends" ~ "Unsure",
         GENFBACK_1 == "Prefer not to say" ~ "Unsure")),
         
         GENFBACK_no_prevent_agree = 
         as.factor(case_when(GENFBACK_2 == "Yes, definitely" ~ "Yes", 
         GENFBACK_2 == "Yes, probably" ~ "Yes",
         GENFBACK_2 == "No, probably not" ~ "No",
         GENFBACK_2 == "No, definitely not" ~ "No",
         GENFBACK_2 == "Not sure / it depends" ~ "No",
         GENFBACK_2 == "Prefer not to say" ~ "No")),
         
         GENFBACK_no_prevent_all = 
         as.factor(case_when(GENFBACK_2 == "Yes, definitely" ~ "Yes", 
         GENFBACK_2 == "Yes, probably" ~ "Yes",
         GENFBACK_2 == "No, probably not" ~ "No",
         GENFBACK_2 == "No, definitely not" ~ "No",
         GENFBACK_2 == "Not sure / it depends" ~ "Unsure",
         GENFBACK_2 == "Prefer not to say" ~ "Unsure")),
         
         GENFBACK_ancestry_agree = 
         as.factor(case_when(GENFBACK_3 == "Yes, definitely" ~ "Yes", 
         GENFBACK_3 == "Yes, probably" ~ "Yes",
         GENFBACK_3 == "No, probably not" ~ "No",
         GENFBACK_3 == "No, definitely not" ~ "No",
         GENFBACK_3 == "Not sure / it depends" ~ "No",
         GENFBACK_3 == "Prefer not to say" ~ "No")),
         
         GENFBACK_ancestry_all = 
         as.factor(case_when(GENFBACK_3 == "Yes, definitely" ~ "Yes", 
         GENFBACK_3 == "Yes, probably" ~ "Yes",
         GENFBACK_3 == "No, probably not" ~ "No",
         GENFBACK_3 == "No, definitely not" ~ "No",
         GENFBACK_3 == "Not sure / it depends" ~ "Unsure",
         GENFBACK_3 == "Prefer not to say" ~ "Unsure")),
         
         MARSTAT = 
         as.factor(case_when(MARSTAT == "Missing reponse" ~ "Missing reponse", 
         MARSTAT == "Married" ~ "Married/civil partnership",
         MARSTAT == "In a same-sex civil partnership" ~ "Married/civil partnership",
         MARSTAT == "Neither" ~ "Neither",
         MARSTAT == "Prefer not to say" ~ "Prefer not to say")))
         
```

## labelling variables

Add variable labels for the new variables and fix some confusing ones for existing variables.

apply_labels function doesnt like character list input, so unfortunately very long function input. 

```{r add variable labels}  

factor_df = apply_labels(factor_df, 
ofhact_agree="Would you take part in it if you were invited to?
Levels: Yes = Yes definitely Yes probably; No =  No, probably not No, definitely not Not sure / it depends", ofhact_all="Would you take part in it if you were invited to?
Levels: Yes = Yes definitely Yes probably; No =  No, probably not No, definitely not; Unsure = Not sure / it depends",
ofhact_unsure="Would you take part in it if you were invited to?
Levels: NA = Yes definitely Yes probably; No =  No, probably not No, definitely not; Unsure = Not sure / it depends",
GENFBACK_prevent_agree="Genetic feedback for conditions that ARE prevetable or treatable (e.g. type 2 diabetes, heart disease)?
Levels: Yes = Yes definitely Yes probably; No =  No, probably not No, definitely not Not sure / it depends, prefer not to say",
GENFBACK_prevent_all="Genetic feedback for conditions that ARE prevetable or treatable (e.g. type 2 diabetes, heart disease)?
Levels: Yes = Yes definitely Yes probably; No =  No, probably not No, definitely not; Unsure = Not sure / it depends, prefer not to say",
GENFBACK_no_prevent_agree="Genetic feedback for conditions that ARE NOT prevetable or treatable (e.g. some types of dementia)?
Levels: Yes = Yes definitely Yes probably; No =  No, probably not No, definitely not Not sure / it depends,prefer not to say",
GENFBACK_no_prevent_all="Genetic feedback for conditions that ARE NOT prevetable or treatable (e.g. some types of dementia)?
Levels: Yes = Yes definitely Yes probably; No =  No, probably not No, definitely not; Unsure = Not sure / it depends,prefer not to say",
GENFBACK_ancestry_agree="Genetic feedback for ancestry?
Levels: Yes = Yes definitely Yes probably; No =  No, probably not No, definitely not Not sure / it depends,prefer not to say",
GENFBACK_ancestry_all="Genetic feedback for ancestry?
Levels: Yes = Yes definitely Yes probably; No =  No, probably not No, definitely not; Unsure = Not sure / it depends,prefer not to say",
OFHBEN_1="OFH will... advance medical research"
,OFHBEN_2="OFH will... better treatments"
,OFHBEN_3="OFH will... early detection"
,OFHBEN_4="OFH will... help me"
,OFHBEN_5="OFH will... help family/friends"
,OFHBEN_6="OFH will... help community"
,OFHBEN_7="OFH will... help people in UK"
,OFHBEN_8="OFH will... help people in world"
,OFHBEN_9="OFH will... help representation of people like me"
,BARRSA_1="Comfortable health info in large database"
,BARRSA_2="Comfortable share health info with OFH"
,BARRSA_3="Comfortable how OFH use health info"
,BARRSA_4="Comfortable OFH access to medical records"
,BARRSB_1="Comfortable academics access to health records"
,BARRSB_2="Comfortable companies access to health records"
,BLOODS_1="Willing give sample if part of routine blood test"
,BLOODS_2="Willing give sample if soley for OFH"
,BLOODS_3="Difficult to give sample on weekday"
,BLOODS_4="Difficult to give sample on weekend"
,PRACBAR_2="have time for 10 min questionnaire"
,PRACBAR_3="have time for 30 min questionnaire")

```

Fix  value label of religiosity variable  for clarity. First print old values and tale to make sure this works as intended.

```{r print old vals and tables}

levels(factor_df$RELIGIOSITY)
table(factor_df$RELIGIOSITY)

```

```{r fix value labels}

levels(factor_df$RELIGIOSITY) <- c("Missing reponse","Practising","Not practising","Not religious") 
levels(factor_df$MARSTAT) <- c("Missing reponse","Married/civil partnership","Neither","Prefer not to say") 
  
```

check this worked as expected

```{r print new vals and tables}

levels(factor_df$RELIGIOSITY)
table(factor_df$RELIGIOSITY)

```

## rename SEX to gender to match question text
We ask about gender, we do not know about biological sex assigned at birth

```{r rename sex}

factor_df <- factor_df %>%
  rename(GENDER=SEX)
```
## Transform to numeric where appropriate

The trust variables are currently unordered factors, but should be numeric (how much do you trust.... on a scale of 0 - 10)

first grab the labels to add back on after the transformation

```{r grab trust labels}

trust_vars <- factor_df %>%
    select(starts_with("TRUST")) %>%
  colnames() 

trust_labels <- dput(sapply(factor_df[trust_vars],label))
```

then transform
```{r transform trust to numeric}

factor_df <- factor_df %>%
  mutate(across(starts_with("TRUST"), 
         ~as.numeric(case_when(. == "0 - Do not trust at all" ~ 0,
                               . == "10 - Trust completely" ~ 10,
                               . == "1" ~ 1,
                               . == "2" ~ 2,
                               . == "3" ~ 3,
                               . == "4" ~ 4,
                               . == "5" ~ 5,
                               . == "6" ~ 6,
                               . == "7" ~ 7,
                               . == "8" ~ 8,
                               . == "9" ~ 9,
                               TRUE ~ NA_real_ ))))

```

add the labels back
```{r add trust labels back}
label(factor_df[trust_vars]) = as.list(trust_labels[match(names(factor_df[trust_vars]), names(trust_labels))])
```

Check this all worked as expected

```{r show trust variables}

factor_df %>% 
  select(starts_with("TRUST")) %>%
  skimr::skim() %>%
  select(skim_type, skim_variable, n_missing, numeric.mean, numeric.sd,numeric.hist)

table(factor_df$TRUSTGEN)
dput(sapply(factor_df[trust_vars],label))
```

## create summed variables 

This will include
* A summed variable summarising ease of use of internet for life admin (DIGPROF vars)
* A summed variable summarising volunteering (PROSO vars)
* A summed variable summarising research participation (sci vars??)
* A summed variable summarising trust in science


### Create vectors for the summary score items

#### Digital proficiency 

**Digital proficiency scoring**

Dont know = 0
Not at all confident = 0
Not very confident = 1
Fairly confident = 2
Very confident = 3

minimum score = 0 (not at all confident on any)
maximum score = 15 (very confident for all)

```{r sum score vectors digi proficiency}

# Digital proficiency
Digprof_cols <- factor_df %>%
  select(contains("DIGPROF")) %>%
  colnames() 

lapply(factor_df[Digprof_cols],label) 

```
    
#### Any lifetime pro social

```{r sum score vectors prosocial ever}
# Volunteering ever
Volunteering.ever_cols <- factor_df %>%
  select(contains("PROSO_"),
         -"PROSO_NONE") %>%
  colnames()

lapply(factor_df[Volunteering.ever_cols],label)

```

####  4 weeks pro social
```{r sum score vectors prosocial 4 weeks}
# Volunteering ever
Volunteering.4_cols <- factor_df %>%
  select(contains("PROSO4W_"),
         -"PROSO4W_NONE") %>%
  colnames()

lapply(factor_df[Volunteering.4_cols],label)

```

#### Scientific trust
```{r sum score vectors science}
# Volunteering 4 weeks
science_cols <- factor_df %>%
  select(contains("SCI"),
         -c("SCIINF","SCIINT")) %>%
  colnames()

lapply(factor_df[science_cols],label)

```

#### research participation

```{r sum score vectors research participation}
# Volunteering 4 weeks
participation_cols <- factor_df %>%
  select(contains("HRES"),
         -c("HRES_NONE","HRES_DK")) %>%
  colnames()

lapply(factor_df[participation_cols],label)

```

### create sum scores.

use column vectors to mutate new columns

#### Digital proficiency 

**Digital proficiency scoring**

Dont know = 0
Not at all confident = 0
Not very confident = 1
Fairly confident = 2
Very confident = 3

minimum score = 0 (not at all confident on any)
maximum score = 15 (very confident for all)

```{r create digital proficiency sum score}

 factor_df <- factor_df %>%
  mutate(DIGPROF_TOTAL = 0 + rowSums(factor_df[Digprof_cols] == "Not very confident") + 
           (rowSums(factor_df[Digprof_cols] == "Fairly confident")*2) +
           (rowSums(factor_df[Digprof_cols] == "Very confident")*3)) 


factor_df = apply_labels(factor_df, 
DIGPROF_TOTAL="Composite score indicating overall ease of use of internet for life admin. Minimum 0 indicating not at all confident and maximum of 15 indicating very confident")
```

#### Pro social 
**Pro social (Ever) and pro social 4 weeks**

Yes = 1
No = 0 

minimum score = 0 (no volunteering ever)
Maximum score = 3 (donated blood, donated money to charity, volunteered EVER)

```{r create prosocial sum scores}

 factor_df <- factor_df %>%
  mutate(PROSO_EVER_TOTAL = 0 + rowSums(factor_df[Volunteering.ever_cols] == "Yes"),
         PROSO4W_TOTAL = 0 + rowSums(factor_df[Volunteering.4_cols] == "Yes"),
         ) 


factor_df = apply_labels(factor_df, 
PROSO_EVER_TOTAL="Composite score indicating number of pro social activities ever undertaken. Minimum score of 0 indicates none of the three were endorsed, maximum of 3 indicates all activities endorsed",
PROSO4W_TOTAL="Composite score indicating number of pro social activities undertaken in the past 4 weeks. Minimum score of 0 indicates none of the three were endorsed, maximum of 3 indicates all activities endorsed")
```

#### Trust in science 

Strongly agree = 2
Agree = 1
Neither agree nor disagree = 0
Disagree -1
Strongly disagree = -2
Don't know = 0

minimum score = -6 (strong distrust of science)
maximum score = 6 (Strong trust in science)
Score of 0 indicates neutrality

```{r create trust in science  sum score}

 factor_df <- factor_df %>%
  mutate(SCITRUST_TOTAL = 0 + (rowSums(factor_df[science_cols] == "Strongly agree") * 2) +
         (rowSums(factor_df[science_cols] == "Agree")) +
         (rowSums(factor_df[science_cols] == "Disagree") * -1) +
         (rowSums(factor_df[science_cols] == "Strongly disagree") * -2)
         ) 


factor_df = apply_labels(factor_df, 
SCITRUST_TOTAL="Composite score indicating trust or distrust in science overall. A negative score indicates greater distrust overall and a positive score indicates greater trust overall.")
```

#### Research participation


Yes = 1
No = 0 

minimum score = 0 (never taken part in health research)
Maximum score = 3 (taken part in clinical trials, focus groups and surveys)

```{r create research participation sum score}

 factor_df <- factor_df %>%
  mutate(HRES_TOTAL = 0 + (rowSums(factor_df[participation_cols] == "Yes"))
         ) 


factor_df = apply_labels(factor_df, 
HRES_TOTAL="Summed score indicating research participation. Minimum value of 0 indicates no previous participation in research, maximum value of 3 indicates previous participation in survey, clinical trials and focus groups.")
```


# Data preparation

prepare lists of variables that we are interested in for data summaries,
and additional lists for predictors and outcomes we want to test in univariable regressions

## Variable lists for analyses
***All variables***
Note, using total score variables instead of individual variables where composites or sum scores exist
```{r list of vars for univariable analyses}
all.vars <- c(
"Black_filter", "Asian_filter", "MDQuintile", "AGE", "AGE_BAND", 
"GENDER", "ETHNICITY", "ETHNICITY_LFS", "NUMPEOPLE", "NUMADULTS", 
"NUMCHILDU16", "COHAB", "COHAB_BINARY", "MARSTAT", "CHILDHERE", 
"NumOwnChildrenU16HH", "OwnChildU16OutsideHH", "HHSTRUCTURE", 
"PLACEINHH", "INTERNET", "DEVICE_SMRTPHNE", "DEVICE_MOBILE", 
"DEVICE_LANDLINE", "DEVICE_TABLET", "DEVICE_CPU", "DEVICE_SMRTTV", 
"DEVICE_GAME", "DEVICE_STREAM", "DEVICE_WEAR", "DEVICE_TOTAL", 
"DIGPROF_TOTAL", "FINNOW", "RELIGIOSITY", "RELIGION", "QUALTYPE", 
"EDUCATION", "DEGREE", "WorkingStatus_PrePandemic", "WorkingStatus_PrePandemic_Binary", 
"WorkingStatus", "WorkingStatus_Binary",
"OCCUPATION_NSSEC", "TENURE", "LIFEEVENT", "PROSO_EVER_TOTAL", 
"PROSO4W_TOTAL","DISABILITY", 
"DISAB1", "DISAB2", "DISABEVER", "GENFAM", "GENTEST", "GENTEST_1", 
"GENTEST_2", "GENTEST_3", "GENTEST_4", "GENTEST_5", "GENTEST_5OPEN", 
"GENTTYP_1", "GENTTYP_2", "GENTTYP_3", "GENTTYP_4", "GENTTYP_5", 
"DISABFAM", "AID", "HEALTH", "HRES_TOTAL","HACT12_1", "HACT12_2", 
"HACT12_3", "HACT12_4", 
"TRUSTGEN", "TRUSTORG_A", "TRUSTORG_B", "TRUSTORG_C", "TRUSTORG_D", 
"TRUSTORG_E", "SCIINT", "SCIINF", "SCITRUST_TOTAL",
"COVRES", "OFHAWARE", "VIDEO", "AUDIO", "UNDERST", "OFHACT", 
"OFHYN_FREQ", "OFHYN_OPEN", "OFHDK_FREQ", "OFHDK_OPEN", "OFHDK2_FREQ", 
"OFHDK2_OPEN", "OFHPAIR_A", "OFHPAIR_B", "OFHPAIR_C", "OFHPAIR_D", 
"OFHPAIR_E", "OFHBEN_1", "OFHBEN_2", "OFHBEN_3", "OFHBEN_4", 
"OFHBEN_5", "OFHBEN_6", "OFHBEN_7", "OFHBEN_8", "OFHBEN_9", "OFHBENCL", 
"BARRSA_1", "BARRSA_2", "BARRSA_3", "BARRSA_4", "BARRSB_1", "BARRSB_2", 
"BLOODS_1", "BLOODS_2", "BLOODS_3", "BLOODS_4", "BLOODS_5", "BLOODS_6", 
"BLOODS_7", "PRACBAR_1", "PRACBAR_2", "PRACBAR_3", "GENFBACK_1", 
"GENFBACK_2", "GENFBACK_3", "PARTNA", "PARTNB", "OFHACT2", "RECONTACT", 
"ofhact_agree", "ofhact_all", "ofhact_unsure", "GENFBACK_prevent_agree", 
"GENFBACK_prevent_all", "GENFBACK_no_prevent_agree", "GENFBACK_no_prevent_all", 
"GENFBACK_ancestry_agree", "GENFBACK_ancestry_all")
```

***demographic characteristics***
```{r list of demographic vars for univariable analyses}
dem.vars <- c(
"Black_filter", "Asian_filter", "MDQuintile", "AGE_BAND", 
"GENDER", "ETHNICITY", "ETHNICITY_LFS", "NUMPEOPLE", "MARSTAT", 
"NumOwnChildrenU16HH", "OwnChildU16OutsideHH", "RELIGIOSITY", "RELIGION", "QUALTYPE", 
"EDUCATION", "DEGREE", "WorkingStatus_PrePandemic", "WorkingStatus_PrePandemic_Binary", 
"WorkingStatus", "WorkingStatus_Binary",
"OCCUPATION_NSSEC", "TENURE")
```

***outcomes***
```{r list of outcome vars for univariable analyses}
primary.outcome.binary <- "ofhact_agree" # intention to participate
primary.outcome.all <- "ofhact_all" #intention to participate, including unsure

gen.outcome.preventable.binary <- "GENFBACK_prevent_agree"
gen.outcome.preventable.all <- "GENFBACK_prevent_all"

gen.outcome.nonpreventable.binary <- "GENFBACK_no_prevent_agree"
gen.outcome.nonpreventable.all <- "GENFBACK_no_prevent_all"

gen.outcome.ancestry.binary <- "GENFBACK_ancestry_agree"
gen.outcome.ancestry.all <- "GENFBACK_ancestry_all"

outcomes <- c("ofhact_agree","ofhact_all",
              "GENFBACK_prevent_agree","GENFBACK_prevent_all",
                  "GENFBACK_no_prevent_agree","GENFBACK_no_prevent_all",
                  "GENFBACK_ancestry_agree","GENFBACK_ancestry_all")
  
```

***independent variables***
```{r list of independent vars for univariable analyses}
pred.participate.vars <- c("LIFEEVENT", "PROSO_EVER_TOTAL","PROSO4W_TOTAL", 
"GENFAM", "GENTEST",
"DISABFAM", "AID", "HEALTH", "HRES_TOTAL",
"HACT12_1", "HACT12_2", "HACT12_3", "HACT12_4", 
"TRUSTGEN", "TRUSTORG_A", "TRUSTORG_B", "TRUSTORG_C", "TRUSTORG_D", 
"TRUSTORG_E", "SCIINT", "SCIINF", "SCITRUST_TOTAL", 
"COVRES", "OFHAWARE", "UNDERST", "OFHACT", 
"OFHPAIR_A", "OFHPAIR_B", "OFHPAIR_C", "OFHPAIR_D", 
"OFHPAIR_E", "OFHBEN_1", "OFHBEN_2", "OFHBEN_3", "OFHBEN_4", 
"OFHBEN_5", "OFHBEN_6", "OFHBEN_7", "OFHBEN_8", "OFHBEN_9", "OFHBENCL", 
"BARRSA_1", "BARRSA_2", "BARRSA_3", "BARRSA_4", "BARRSB_1", "BARRSB_2", 
"BLOODS_1", "BLOODS_2", "BLOODS_3", "BLOODS_4", "BLOODS_5", "BLOODS_6", 
"BLOODS_7", "PRACBAR_1", "PRACBAR_2", "PRACBAR_3", "GENFBACK_1", 
"GENFBACK_2", "GENFBACK_3", "PARTNA", "PARTNB", "OFHACT2", "RECONTACT", 
 "GENFBACK_prevent_agree", 
"GENFBACK_prevent_all", "GENFBACK_no_prevent_agree", "GENFBACK_no_prevent_all", 
"GENFBACK_ancestry_agree", "GENFBACK_ancestry_all","DISABILITY", 
"DISAB1",  "DISABEVER")


  
pred.gen.vars <-c( "INTERNET", "DEVICE_SMRTPHNE", "DEVICE_MOBILE", 
 "DEVICE_TABLET", "DEVICE_CPU", "DEVICE_WEAR", "DEVICE_TOTAL", 
"DIGPROF_TOTAL", "FINNOW", "RELIGIOSITY", "RELIGION", 
"EDUCATION",  "WorkingStatus_Binary","OCCUPATION_NSSEC",
 "LIFEEVENT", "PROSO_EVER_TOTAL","PROSO4W_TOTAL",  "GENFAM", "GENTEST", 
"DISABFAM", "AID", "HEALTH", "HRES_TOTAL","HACT12_1", "HACT12_2", "HACT12_3", "HACT12_4", 
"TRUSTGEN", "TRUSTORG_A", "TRUSTORG_B", "TRUSTORG_C", "TRUSTORG_D", 
"TRUSTORG_E", "SCIINT", "SCIINF", "SCITRUST_TOTAL", 
"COVRES", "OFHAWARE", "UNDERST", "OFHACT", 
 "OFHPAIR_A", "OFHPAIR_B", "OFHPAIR_C", "OFHPAIR_D", 
"OFHPAIR_E", "OFHBEN_1", "OFHBEN_2", "OFHBEN_3", "OFHBEN_4", 
"OFHBEN_5", "OFHBEN_6", "OFHBEN_7", "OFHBEN_8", "OFHBEN_9", "OFHBENCL", 
"BARRSA_1", "BARRSA_2", "BARRSA_3", "BARRSA_4", "BARRSB_1", "BARRSB_2", 
"BLOODS_1", "BLOODS_2", "BLOODS_3", "BLOODS_4", "BLOODS_5", "BLOODS_6", 
"BLOODS_7", "PRACBAR_1", "PRACBAR_2", "PRACBAR_3",  
"PARTNA", "PARTNB", "OFHACT2", "RECONTACT","ofhact_agree", "ofhact_all", "ofhact_unsure","DISABILITY", 
"DISAB1",  "DISABEVER")

all.pred.vars <- c(
"MDQuintile",  "AGE_BAND", 
"GENDER", "ETHNICITY_LFS", "NUMPEOPLE",
"NumOwnChildrenU16HH", "OwnChildU16OutsideHH", "INTERNET", "DEVICE_SMRTPHNE", "DEVICE_MOBILE", 
 "DEVICE_TABLET", "DEVICE_CPU", "DEVICE_WEAR", "DEVICE_TOTAL", 
"DIGPROF_TOTAL", "FINNOW", "RELIGIOSITY",  "OCCUPATION_NSSEC",
"EDUCATION",  "WorkingStatus_Binary",  
 "LIFEEVENT", "PROSO_EVER_TOTAL","PROSO4W_TOTAL", "GENFAM", "GENTEST",  
"DISABFAM", "AID", "HEALTH", "HRES_TOTAL","HACT12_1", "HACT12_2", "HACT12_3", "HACT12_4", 
"TRUSTGEN", "TRUSTORG_A", "TRUSTORG_B", "TRUSTORG_C", "TRUSTORG_D", 
"TRUSTORG_E", "SCIINT", "SCIINF", "SCITRUST_TOTAL", 
"COVRES", "OFHAWARE", "UNDERST", "OFHACT", 
 "OFHPAIR_A", "OFHPAIR_B", "OFHPAIR_C", "OFHPAIR_D", 
"OFHPAIR_E", "OFHBEN_1", "OFHBEN_2", "OFHBEN_3", "OFHBEN_4", 
"OFHBEN_5", "OFHBEN_6", "OFHBEN_7", "OFHBEN_8", "OFHBEN_9", "OFHBENCL", 
"BARRSA_1", "BARRSA_2", "BARRSA_3", "BARRSA_4", "BARRSB_1", "BARRSB_2", 
"BLOODS_1", "BLOODS_2", "BLOODS_3", "BLOODS_4", "BLOODS_5", "BLOODS_6", 
"BLOODS_7", "PRACBAR_1", "PRACBAR_2", "PRACBAR_3",  
"PARTNA", "PARTNB", "OFHACT2", "RECONTACT","DISABILITY", 
"DISAB1",  "DISABEVER")

gated.pred.vars <- c("RELIGION","GENTEST_1", 
"GENTEST_2", "GENTEST_3", "GENTEST_4", "GENTEST_5", "GENTEST_5OPEN", 
"GENTTYP_1", "GENTTYP_2", "GENTTYP_3", "GENTTYP_4", "GENTTYP_5",
"OFHYN_FREQ", "OFHYN_OPEN", "OFHDK_FREQ", "OFHDK_OPEN", "OFHDK2_FREQ", 
"OFHDK2_OPEN","DISAB2")
```

##### DOING/To DO
create an aggreagte score for seeking information about different things 
collapse occupation NSEC so that sub categories are all under the same bigger category 
fix multinomial regression

# Data summaries {.tabset}

get histograms and frequency tables for all variables


## demographic variables
```{r freq demographic variables}

for (i in dem.vars){
  frequency_and_plot(factor_df,all_of(i))
}
```

## outcome variables
```{r summaries of outcome variables}

for (i in outcomes){
  frequency_and_plot(factor_df,i)
}

```
## predictor variables
```{r summaries of predictor variables}

for (i in all.pred.vars){
  frequency_and_plot(factor_df,i)
}

```

# Analysis prep
## recode missing data

recode don't know, prefer not to say and and missing response as NA (missing data) in the analytic data set. 

Retain don't know and prefer not to say in factor df for summaries. 

Capture a list of variable labels as these get lost in the NA process

```{r capture labels, results='hide'}
label_list <- dput(sapply(factor_df,label))
```

first remove missing data and set to NA in the factor dataset

```{r set missing data to NA}


factor_df <- factor_df %>%
  mutate(across(where(is.factor), 
                ~as.factor(case_when(. =="Missing reponse" ~ NA_character_, 
                                     TRUE ~ as.character(.)))))
  
```



then change all (dont know, prefer not to say, missing) to NA for the analytic data set

```{r set all non responses to NA}

regression_df <- factor_df %>%
  mutate(across(where(is.factor), 
                ~as.factor(case_when(. =="Don't know" ~ NA_character_,
                                     . =="Prefer not to say" ~ NA_character_,
                                     TRUE ~ as.character(.)))))
```


## set reference categories

### predictors

Make the largest group the reference category using custom function

```{r set largest ref category}

regression_df <- regression_df %>%
  mutate(across(where(is.factor), 
                ~set.largest.ref(.)))
```

### outcomes

s specific reference variables for my outcomes reflecting the outcome of greatest interest

```{r}

regression_df$ofhact_agree <-  relevel(regression_df$ofhact_agree,ref= "No")
regression_df$ofhact_all <-  relevel(regression_df$ofhact_all,ref= "No")

regression_df$GENFBACK_prevent_agree <-  relevel(regression_df$GENFBACK_prevent_agree,ref= "No")
regression_df$GENFBACK_prevent_all <-  relevel(regression_df$GENFBACK_prevent_all,ref= "No")

regression_df$GENFBACK_no_prevent_agree <-  relevel(regression_df$GENFBACK_no_prevent_agree,ref= "No")
regression_df$GENFBACK_no_prevent_all <-  relevel(regression_df$GENFBACK_no_prevent_all,ref= "No")

regression_df$GENFBACK_ancestry_agree <-  relevel(regression_df$GENFBACK_ancestry_agree,ref= "No")
regression_df$GENFBACK_ancestry_all <-  relevel(regression_df$GENFBACK_ancestry_all,ref= "No")


```


## add labels back to data set

```{r add labels to factor df}

label(factor_df) = as.list(label_list[match(names(factor_df), names(label_list))])
label(regression_df) = as.list(label_list[match(names(regression_df), names(label_list))])

```


# univariable regressions 
Replicate Alice's regressions. identify which demographic features are important to use as covariates in multivariable regressions. 

* numeric outcomes: linear regression   

* binary outcomes:binomial logistic regression with estimates converted to OR and OR adjusted standard errors using coefficient variance (see https://www.andrewheiss.com/blog/2016/04/25/convert-logistic-regression-standard-errors-to-odds-ratios-with-r/)      

* 3 or more levels in outcome: multinomial regression    


## demographic predictors

Run univariable regressions and output each set as a new row in a final summary table

### Binomial logistic

predicting binarised outcomes (yes, no)
```{r create univar binary logistic, results="asis"}

for (x in dem.vars){
  do.univariable.binomial.regression(regression_df,"ofhact_agree",x)
}

for (x in dem.vars){
  do.univariable.binomial.regression(regression_df,"GENFBACK_prevent_agree",x)
}

for (x in dem.vars){
  do.univariable.binomial.regression(regression_df,"GENFBACK_no_prevent_agree",x)
}

for (x in dem.vars){
  do.univariable.binomial.regression(regression_df,"GENFBACK_ancestry_agree",x)
}

```

### Multinomial logistic

predicting categorical outcomes (Yes, No, Unusre)
```{r create univar multinomials, results="asis"}

for (x in dem.vars){
  print("#####")
  do.univariable.multinomial.regression(regression_df,"ofhact_all",x)
}

for (x in dem.vars){
    print("#####")
  do.univariable.multinomial.regression(regression_df,"GENFBACK_prevent_all",x)
}

for (x in dem.vars){
    print("#####")
  do.univariable.multinomial.regression(regression_df,"GENFBACK_no_prevent_all",x)
}

for (x in dem.vars){
    print("#####")
  do.univariable.multinomial.regression(regression_df,"GENFBACK_ancestry_all",x)
}

```

# multivariable regressions

There will be three models for each outcome.

1) all demographic predictors that are significant in univariable models (where two or more predictors are similar, will use the one that was the strongest univariable predictor)
2) each individual non demographic predictor including significant demographic predictors as covariates
3) all significant predictors and demographic predictors in a single model


## Model 1: all demographic predictors to identify strongest independent predictors

Significant demographic predictors for each outcome are as follows (significance adjusted fro number of levels. i.e. a predictor where 8 levels are tested threshold would be 0.05/8=0.006)

Select the strongest univariable predictor where one or more similar variables/variables indexing the smae thing overlap


### identify selected Yes v No binary outcomes
#### Taking part in our future health binary
'*' indicates variables dropped where other better predictors of an outcome exist

* Asian_filter (Asian respondents less likely to take part relative to all other ethnicity)   
* MDQuintile (The higher the quintile the more likely to take part. Higher indicates less deprived)   
* AGE_BAND (younger groups;18-25; less like to take part compared to largest respondent group - 35-44. Older; 45-54 and 65-74; more likely to take part)   
* ETHNICITY (White British more likely to take part than any other group) Will include this rather than collapsed for now as there are distinct effects in smaller subgroups. Will consider power and whether better to collapse at a later stage. '*'   
* MARSTAT (People who are neither married nor in a civil partnership are less likely to take part relative to married/civil partnered people)   
* QUALTYPE (Those without educational and vocational qualifications less likely to take part) '*'      
* EDUCATION (Those with less than degree level less likely to take part than those with degree level) '*'      
* DEGREE (Those without a degree and less likely to take part than those with a degree)   
* WorkingStatus_PrePandemic (those who were full time students or unemployed pre pandemic less likely to take part) '*'   
* WorkingStatus_PrePandemic_Binary (those who were unemployed less likely to take part relative to employed or on mt leave) '*'   
* WorkingStatus (those who are full time students or unemployed less likely to take part) '*'  
* WorkingStatus_Binary (those who are not working or on mat leave less likely to take part)    
* TENURE (People who own their property outright are more likely to take part than those who rent)

#### Receive genetic feedback about things preventable or treatable binary

* Black_filter (Black respondents less likely to want feedback relative to all other ethnicity)   
* MDQuintile (The higher the quintile the more likely to want feedbackt. Higher indicates less deprived)   
* AGE_BAND (older groups ; 65 +; less to want feedback compared to largest respondent group - 35-44)   
* ETHNICITY_LFS (Black respondents less likely to want feedback compared to white respondents) Do not appear to be differences driven by communities and will use LFS collapsed ethnicity here. '*'   
* MARSTAT (People who are neither married nor in a civil partnership are less likely to want feedback relative to married/civil partnered people)  
* RELIGIOSITY (people who are practicing their religion are less likely to want feedback relative to those who re not religious)    
* RELIGION (people of the Muslim faith are less likely than those with no religion to want feedback) ***note*** a lot of missing data here.Will likely include as a sensitivity model, but wont include in main as will result in too many dropped cases.
* QUALTYPE (Those without educational and vocational qualifications or without any degree less likely to want feedback) '*'  
* EDUCATION (Those with less than degree level less likely to want feedback than those with degree level) '*'  
* DEGREE (Those without a degree and less likely to want feedback than those with a degree)   
* WorkingStatus_PrePandemic (those who were retired pre pandemic less likely to want feedback) '*'   
* WorkingStatus_PrePandemic_Binary (those who were unemployed less likely to want feedback relative to employed or on mt leave) '*'   
* WorkingStatus (those who are retired less likely to want feedback)   
* WorkingStatus_Binary (those who are not working or on mat leave less likely to want feedback)   
* TENURE (People who own their property with a mortgage more likely to want feedback than those who rent)

#### Receive genetic feedback about things that are not preventable or treatable binary

* AGE_BAND (older groups ; 65 +; less to want feedback compared to largest respondent group - 35-44)   
* GENDER (men more likely to want feedback relative to women)
* ETHNICITY (People from White other backgrounds more likely to want feedback compared wo White British)       
* MARSTAT (People who are neither married nor in a civil partnership are less likely to want feedback relative to married/civil partnered people)  
* QUALTYPE (Those without educational and vocational qualifications or without any degree less likely to want feedback) '*'   
* EDUCATION (Those with less than degree level less likely to want feedback than those with degree level) '*'   
* DEGREE (Those without a degree and less likely to want feedback than those with a degree)    
* WorkingStatus_PrePandemic (those who were retired  pre pandemic less likely to want feedback) '*'   
* WorkingStatus_PrePandemic_Binary (those who were unemployed less likely to want feedback relative to employed or on mt leave) '*'   
* WorkingStatus (those who are retired less likely to want feedback)    
* WorkingStatus_Binary (those who are not working or on mat leave less likely to want feedback)   

#### Receive genetic feedback ancestry binary

* Black_filter (Black respondents less likely to want ancestry relative to all other ethnicity)    
* Asian_filter (Asian respondents less likely to want ancestry relative to all other ethnicity)   
* MDQuintile (higher quintile more likely to want ancestry; higher is less deprived)    
* GENDER (men more likely to want ancestry relative to women)
* ETHNICITY_LFS (People from White other backgrounds more likely to want ancestry compared to many other ethnicities) '*'       
* MARSTAT (People who are neither married nor in a civil partnership are less likely to want ancestry relative to married/civil partnered people)      
* RELIGIOSITY (people who are practicing religios are more likely than not religious to want ancestry)    
* RELIGION (people of the Muslim faith are less likely than those with no religion to want ancestry) ***note*** a lot of missing data here.Will likely include as a sensitivity model, but wont include in main as will result in too many dropped cases. 
* QUALTYPE (Those without educational and vocational qualifications or less likely to want ancestry) '*'   
* EDUCATION (Those with less than degree level less likely to want ancestry than those with degree level) '*'   
* DEGREE (Those without a degree and less likely to want ancestry than those with a degree)   
* WorkingStatus_PrePandemic (those who were looking after family or home or doing something else less likely to want ancestry) '*'   
* WorkingStatus_PrePandemic_Binary (those who were unemployed less likely to want ancestry relative to employed or on mt leave) '*'   
* WorkingStatus (those who are looking after family or home less likely to want ancestry) '*'   
* WorkingStatus_Binary (those who are not working or on mat leave less likely to want ancestry)   


### identify selected  Yes v No v Unsure multi-level outcomes
#### Taking part in our future health: Yes, No, Unsure

* MDQuintile (The higher the quintile the less likely to be unsure about taking part relative to not. Higher indicates less deprived)   
* AGE_BAND (oldder groupd less likey to be unsure about taking part compared to not taking part relative to 35-44yr olds)   
* GENDER (Men likely to be unsure relative to women)
* ETHNICITY (White British more likely to take part than black caribbean or pakistani) Will include this rather than collapsed for now as there are distinct effects in smaller subgroups. Will consider power and whether better to collapse at a later stage.   
* MARSTAT (People who are neither married nor in a civil partnership are less likely to be unsure or to take part relative to married/civil partnered people)   
* QUALTYPE (Those without educational and vocational qualifications less likely to take part) '*'   
* EDUCATION (Those with less than degree level less likely to take part or be unsure than those with degree level) '*'   
* DEGREE (Those without a degree and less likely to take part or be unsure (compared to no) than those with a degree)   
* WorkingStatus_PrePandemic (those who were full time students less likely to take part, those who are retired are less likely to be unsure ) '*'   
* WorkingStatus_PrePandemic_Binary (those who were unemployed less likely to take part relative to employed or on mt leave) '*'   
* WorkingStatus (those who were full time students less likely to take part, those who are retired are less likely to be unsure ) '*'     
* WorkingStatus_Binary (those who are not working or on mat leave less likely to take part)   
* TENURE (People who own their property outright are more likely to be sunure about taking part than those who rent)

#### Receive genetic feedback about things preventable or treatable: Yes, No, Unsure

* Black_filter (Black respondents less likely to want feedback relative to all other ethnicity)   
* AGE_BAND (older groups ; 65 +; less to want feedback compared to largest respondent group - 35-44)   
* MARSTAT (People who are neither married nor in a civil partnership are less likely to want feedback relative to married/civil partnered people)  
* RELIGIOSITY (people who are practicing their religion are less likely to want feedback relative to those who re not religious)    
* QUALTYPE (Those without educational and vocational qualifications or without any degree less likely to want feedback) '*'   
* EDUCATION (Those with less than degree level less likely to want feedback than those with degree level) '*'   
* DEGREE (Those without a degree and less likely to want feedback than those with a degree)   
* WorkingStatus_PrePandemic (those who were retired pre pandemic less likely to want feedback) '*'   
* WorkingStatus_PrePandemic_Binary (those who were unemployed less likely to want feedback relative to employed or on mt leave) '*'   
* WorkingStatus (those who are retired less likely to want feedback) '*'   
* WorkingStatus_Binary (those who are not working or on mat leave less likely to want feedback)   
* TENURE (People who own their property with a mortgage more likely to want feedback than those who rent)

#### Receive genetic feedback about things that are not preventable or treatable: Yes, No, Unsure

* AGE_BAND (75 +; less to want feedback compared to largest respondent group - 35-44)   
* ETHNICITY (People from White other backgrounds more likely to want feedback compared wo White British)       
* QUALTYPE (Those without educational and vocational qualifications or without any degree less likely to want feedback) '*'   
* EDUCATION (Those with less than degree level less likely to want feedback than those with degree level) '*'   
* DEGREE (Those without a degree and less likely to want feedback than those with a degree)   
* WorkingStatus_PrePandemic (those who were retired  pre pandemic less likely to want feedback) '*'  
* WorkingStatus_PrePandemic_Binary (those who were unemployed less likely to want feedback relative to employed or on mt leave) '*'  
* WorkingStatus (those who are retired less likely to want feedback)    
* WorkingStatus_Binary (those who are not working or on mat leave less likely to want feedback) '*'  

#### Receive genetic feedback ancestry binary: Yes, No, Unsure

* Black_filter (Black respondents less likely to want ancestry relative to all other ethnicity)   
* Asian_filter (Asian respondents less likely to want ancestry relative to all other ethnicity)   
* ETHNICITY_LFS (People from White other backgrounds more likely to want ancestry compared to many other ethnicities) '*'       
* MARSTAT (People who are neither married nor in a civil partnership are less likely to want ancestry relative to married/civil partnered people)  
* RELIGIOSITY (people who are practicing religios are more likely than not religious to want ancestry)    
* RELIGION (people of the Muslim faith are less likely than those with no religion to want ancestry) ***note*** a lot of missing data here.Will likely include as a sensitivity model, but wont include in main as will result in too many dropped cases. 
* QUALTYPE (Those without educational and vocational qualifications or less likely to want ancestry)'*'  
* EDUCATION (Those with less than degree level less likely to want ancestry than those with degree level)'*'   
* DEGREE (Those without a degree and less likely to want ancestry than those with a degree)   
* WorkingStatus_PrePandemic_Binary (those who were unemployed less likely to want ancestry relative to employed or on mt leave) '*'   
* WorkingStatus_Binary (those who are not working or on mat leave less likely to want ancestry)   

####  set variable lists for significant demographic predictors for each outcome

I am dropping marital status for now as these people are all missing their MDQuintile data, and there are very few of them. Will do later sensitivty analyses in this group
```{r set up outcome predictor demographic}

## binary
demo.pred.takepart.binary <- c("Asian_filter", "MDQuintile", "AGE_BAND", 
                                 "DEGREE", 
                               "WorkingStatus_Binary",  
                               "TENURE")

demo.pred.takepart.nocont <- c("Asian_filter", "AGE_BAND", 
                               "ETHNICITY",   "DEGREE", 
                               "WorkingStatus",  
                               "TENURE")

demo.pred.prevent.binary <- c("Black_filter", "MDQuintile", "AGE_BAND", 
                           
                              "RELIGIOSITY", "DEGREE", 
                              "WorkingStatus", "WorkingStatus_Binary", 
                              "TENURE")

demo.pred.noprevent.binary <- c("AGE_BAND", "GENDER", 
                                "ETHNICITY","DEGREE",  
                                "WorkingStatus", "WorkingStatus_Binary")

demo.pred.ancestry.binary <- c("Black_filter", "Asian_filter", 
                                                    "MDQuintile", "GENDER", 
                                                    "RELIGIOSITY", "DEGREE", "WorkingStatus_Binary")

demo.pred.ancestry.binary.religion.sensitivity <- c("Black_filter", "Asian_filter", 
                                                    "MDQuintile", "GENDER", 
                                                    "RELIGIOSITY","Religion", "DEGREE", "WorkingStatus_Binary")

## categorical
demo.pred.takepart.multi <- c( "MDQuintile", "AGE_BAND", "GENDER", 
                               "Asian_filter",    "DEGREE", 
                               "WorkingStatus_Binary","TENURE")

demo.pred.prevent.multi <- c("Black_filter", "AGE_BAND", 
                             "RELIGIOSITY",   "DEGREE", 
                              "WorkingStatus_Binary", "TENURE")

demo.pred.noprevent.multi <- c( "AGE_BAND", "ETHNICITY", "DEGREE",  "WorkingStatus")

demo.pred.ancestry.multi <- c("Black_filter", "Asian_filter",
                              "RELIGIOSITY", 
                              "DEGREE", 
                              "WorkingStatus_Binary")

demo.pred.ancestry.multi.religion.sensitivity <- c("Black_filter","Asian_filter",
                               "RELIGIOSITY", "RELIGION", "DEGREE",
                              "WorkingStatus_Binary")
```



### binomial regression

for the binary outcomes and the demographic predictors

```{r run binomial multivariable,results='asis'}
 
do.multivariable.binomial.regression(regression_df,"ofhact_agree",demo.pred.takepart.binary)

do.multivariable.binomial.regression(regression_df,"GENFBACK_prevent_agree",demo.pred.prevent.binary)

do.multivariable.binomial.regression(regression_df,"GENFBACK_no_prevent_agree",demo.pred.noprevent.binary)

do.multivariable.binomial.regression(regression_df,"GENFBACK_ancestry_agree",demo.pred.ancestry.binary)

```

### Multinomial regression

for the binary outcomes and the demographic predictors

```{r run multinomial multivariable,results='asis',warning=FALSE}
 

do.multivariable.multinomial.regression(regression_df,"ofhact_all",demo.pred.takepart.multi)


do.multivariable.multinomial.regression(regression_df,"GENFBACK_prevent_all",demo.pred.prevent.multi)


do.multivariable.multinomial.regression(regression_df,"GENFBACK_no_prevent_all",demo.pred.noprevent.multi)


do.multivariable.multinomial.regression(regression_df,"GENFBACK_ancestry_all",demo.pred.ancestry.multi)

```

## final list of covariates for each model

based on which are significant predictors of the outcome when controlling for others

## Intention to participate

### binary covariates
Significant demographic predictors to be used as covariates are:

* Relative to people who do no identify as Asian, people who identify as Asian in ethnicity are less likely to say they want to take part   
* Relative to people who are 35-44, people who are 18-24 are less likely tosay they want to take part. People who are 45-54 are more likely to say they want to take part    
* Relative to people without a degree level education, people with a degree are more likely to say they want to take part.

### Multi covariates
Significant demographic predictors to be used as covariates are:

* Relative to people who do no identify as Asian, people who identify as Asian in ethnicity are less likely to say they want to take part. They are equally likely to be unsure about participation.
* Relative to people who are 35-44, people who are 18-24 are less likely to say they want to take part. People who are 45-54 are more likely to be unsure about taking part, rather than saying they do not want to take part. 
* Relative to people without a degree level education, people with a degree are more likely to say they want to take part, and more likely to say they are unsure rather than saying no outright.    
* Whilst there are no gender differences in how likely respondents are to say yes versus no to participation, men are more likely to say no outright as opposed to being unsure than women

```{r significant covariate list}

takepart.binary.covariates <- c("Asian_filter","AGE_BAND","DEGREE")
takepart.multi.covariates <- c("Asian_filter","AGE_BAND","DEGREE","GENDER")
  
```

## Model 2: each predictor with significant demographic predictors as covariates

### Binary (yes/no)
```{r run single predictor binomial with covariates, results='asis'}

for (x in pred.participate.vars){
  do.multivariable.binomial.regression(regression_df,"ofhact_agree",append(takepart.binary.covariates, x))
}



```

### Categorical (yes/no/unsure)
```{r run single predictor multinomial with covariates, results='asis'}

for (x in pred.participate.vars){
  do.multivariable.binomial.regression(regression_df,"ofhact_all",append(takepart.multi.covariates, x))
}

```


# Notes and thoughts

## marital status

* Very few people who are not married or in a civil partnership (6% of the whole sample!). ALL of these are missing their IMD quintile data   

## 

## 


