---
title: "Follow on analysis of Kantar Public Attitude Tracker datat 2021"
author: "K L Purves"
date: '`r format(Sys.time(), "%d %B, %Y")`'

output:
  html_document:
    keep_md: true # save images
    self_contained: true
    code_folding: hide
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float:
      collapsed: false
    number_sections: false
    highlight: monochrome
    theme: cerulean


html_notebook:
  theme: cerulean
toc: yes
---


# set up

## Environment
```{r, include=FALSE}
# clear global environment
remove(list = ls())
```


```{r setup, warning=FALSE,echo=FALSE}

# source in all functions in the function library folder
files.sources = paste0("./functions/",list.files("./functions"))
sapply(files.sources, source)

knitr::opts_chunk$set(echo = TRUE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)


# this chunk installs any required packages if you dont already have them in your local library. 
# List of required package names

packages <- c("ggplot2","gtsummary","kableExtra", 
              "purrr", "skimr","readr",
              "readxl","psych",
              "haven", "expss",
              "summarytools","stringr",
              "dplyr", "tidyr")

# apply function to install and load functions as needed. Prints version to screen.
# see function library for code (../functions)
load_packages(packages)



```

Set up ggplot theme for the plots

```{r ggplot theme}

theme_personal <-  function(){theme(
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    axis.title.y = element_blank(), 
    legend.background = element_blank(),
    legend.box.background = element_blank(),
    panel.background = element_blank(), 
    panel.grid.minor.y = element_line(
      colour = "gray",
      linetype = "dashed",
      size = 0.1
      ),
    panel.grid.major.y = element_line(
      colour = "gray",
      linetype = "dashed",
      size = 0.2
      ),
    axis.ticks = element_blank()
    )}

```
# read in raw data

```{r read in raw data}
#import data
df <- read_sav("/Users/kirstinpurves/Library/CloudStorage/OneDrive-SharedLibraries-OurFutureHealth/Main Share - Documents/Our Future Health - Project Team/Behavioural Science/Public attitudes survey 2021/Raw data DO NOT EDIT/262323129-40C_Our Future Health_Dataset_FINAL.sav")
```

skim the data for missingness, completeness and unique values

```{r quick view of file structure and contents, warning=FALSE}

skim(df)

```

Turn character variables into factors using labels instead of values. Use is.labelled function from custom function library

```{r convert to labelled factor}

factor_df <- df %>%
  mutate_if(is.labelled,as_factor)
          
```

Skim new factor labelled data. We can use this for anything where labels are useful. Retain original df for dummy coding.

```{r skim factor df}

skim(factor_df)
```

# Data cleaning

Aligned with Alice's approach. Create the same variables and recode in the same way she did in the preliminary analyses so I can extend these.

## create new  variables dichotomousing or collapsing groups

Would take part in our future health (**OFHACT**)

*dichotomous (Yes, no + unsure)*
**ofhact_agree**

*three groups (Yes, No, Unsure)*
**ofhact_all**

*unsure vs no*
**ofhact_unsure**


Would want genetic feedback for preventable or treatable condition (**GENFBACK_1**)

*dichotomous (yes, no + unsure)*
**GENFBACK_prevent_agree**


*three groups (yes, no, unsure)*
**GENFBACK_prevent_all**

Would want genetic feedback for NOT preventable or treatable condition (**GENFBACK_2**)

*dichotomous (yes, no + unsure*
**GENFBACK_no_prevent_agree**


*three groups (Yes, no, unsure)*
**GENFBACK_no_prevent_all**

Would want genetic feedback for ancestry (**GENFBACK_3**)

*dichotomous (yes, no + unsure*
**GENFBACK_ancestry_agree**


*three groups (Yes, no, unsure)*
**GENFBACK_ancestry_all**


```{r create new variables}

factor_df <- factor_df %>%
  mutate(ofhact_agree = 
         as.factor(case_when(OFHACT == "Yes definitely" ~ "Yes", 
         OFHACT == "Yes probably" ~ "Yes",
         OFHACT == "No, probably not" ~ "No",
         OFHACT == "No, definitely not" ~ "No",
         OFHACT == "Not sure / it depends" ~ "No")),
         
         ofhact_all = 
         as.factor(case_when(OFHACT == "Yes definitely" ~ "Yes", 
         OFHACT == "Yes probably" ~ "Yes",
         OFHACT == "No, probably not" ~ "No",
         OFHACT == "No, definitely not" ~ "No",
         OFHACT == "Not sure / it depends" ~ "Unsure")),
         
         ofhact_unsure = 
         as.factor(case_when(OFHACT == "Yes definitely" ~ NA_character_, 
         OFHACT == "Yes probably" ~ NA_character_,
         OFHACT == "No, probably not" ~ "No",
         OFHACT == "No, definitely not" ~ "No",
         OFHACT == "Not sure / it depends" ~ "Unsure")),
         
         GENFBACK_prevent_agree = 
         as.factor(case_when(GENFBACK_1 == "Yes definitely" ~ "Yes", 
         GENFBACK_1 == "Yes probably" ~ "Yes",
         GENFBACK_1 == "No, probably not" ~ "No",
         GENFBACK_1 == "No, definitely not" ~ "No",
         GENFBACK_1 == "Not sure / it depends" ~ "No",
         GENFBACK_1 == "Prefer not to say" ~ "Prefer not to say")),
         
         GENFBACK_prevent_all = 
         as.factor(case_when(GENFBACK_1 == "Yes definitely" ~ "Yes", 
         GENFBACK_1 == "Yes probably" ~ "Yes",
         GENFBACK_1 == "No, probably not" ~ "No",
         GENFBACK_1 == "No, definitely not" ~ "No",
         GENFBACK_1 == "Not sure / it depends" ~ "Unsure",
         GENFBACK_1 == "Prefer not to say" ~ "Prefer not to say")),
         
         GENFBACK_no_prevent_agree = 
         as.factor(case_when(GENFBACK_2 == "Yes definitely" ~ "Yes", 
         GENFBACK_2 == "Yes probably" ~ "Yes",
         GENFBACK_2 == "No, probably not" ~ "No",
         GENFBACK_2 == "No, definitely not" ~ "No",
         GENFBACK_2 == "Not sure / it depends" ~ "No",
         GENFBACK_2 == "Prefer not to say" ~ "Prefer not to say")),
         
         GENFBACK_no_prevent_all = 
         as.factor(case_when(GENFBACK_2 == "Yes definitely" ~ "Yes", 
         GENFBACK_2 == "Yes probably" ~ "Yes",
         GENFBACK_2 == "No, probably not" ~ "No",
         GENFBACK_2 == "No, definitely not" ~ "No",
         GENFBACK_2 == "Not sure / it depends" ~ "Unsure",
         GENFBACK_2 == "Prefer not to say" ~ "Prefer not to say")),
         
         GENFBACK_ancestry_agree = 
         as.factor(case_when(GENFBACK_3 == "Yes definitely" ~ "Yes", 
         GENFBACK_3 == "Yes probably" ~ "Yes",
         GENFBACK_3 == "No, probably not" ~ "No",
         GENFBACK_3 == "No, definitely not" ~ "No",
         GENFBACK_3 == "Not sure / it depends" ~ "No",
         GENFBACK_3 == "Prefer not to say" ~ "Prefer not to say")),
         
         GENFBACK_ancestry_all = 
         as.factor(case_when(GENFBACK_3 == "Yes definitely" ~ "Yes", 
         GENFBACK_3 == "Yes probably" ~ "Yes",
         GENFBACK_3 == "No, probably not" ~ "No",
         GENFBACK_3 == "No, definitely not" ~ "No",
         GENFBACK_3 == "Not sure / it depends" ~ "Unsure",
         GENFBACK_3 == "Prefer not to say" ~ "Prefer not to say")),
         
         MARSTAT = 
         as.factor(case_when(MARSTAT == "Missing reponse" ~ "Missing reponse", 
         MARSTAT == "Married" ~ "Married/civil partnership",
         MARSTAT == "In a same-sex civil partnership" ~ "Married/civil partnership",
         MARSTAT == "Neither" ~ "Neither",
         MARSTAT == "Prefer not to say" ~ "Prefer not to say")))
         
```

## labelling variables

Add variable labels for the new variables and fix some confusing ones for existing variables.

apply_labels function doesnt like character list input, so unfortunately very long function input. 

```{r add variable labels}  

factor_df = apply_labels(factor_df, 
ofhact_agree="Based on what you now know about the Our Future Health research programme, would you take part in it if you were invited to?
Levels: Yes = Yes definitely Yes probably; No =  No, probably not No, definitely not Not sure / it depends", ofhact_all="Based on what you now know about the Our Future Health research programme, would you take part in it if you were invited to?
Levels: Yes = Yes definitely Yes probably; No =  No, probably not No, definitely not; Unsure = Not sure / it depends",
ofhact_unsure="Based on what you now know about the Our Future Health research programme, would you take part in it if you were invited to?
Levels: NA = Yes definitely Yes probably; No =  No, probably not No, definitely not; Unsure = Not sure / it depends",
GENFBACK_prevent_agree="Genetic feedback for conditions that ARE prevetable or treatable (e.g. type 2 diabetes, heart disease)?
Levels: Yes = Yes definitely Yes probably; No =  No, probably not No, definitely not Not sure / it depends",
GENFBACK_prevent_all="Genetic feedback for conditions that ARE prevetable or treatable (e.g. type 2 diabetes, heart disease)?
Levels: Yes = Yes definitely Yes probably; No =  No, probably not No, definitely not; Unsure = Not sure / it depends",
GENFBACK_no_prevent_agree="Genetic feedback for conditions that ARE NOT prevetable or treatable (e.g. some types of dementia)?
Levels: Yes = Yes definitely Yes probably; No =  No, probably not No, definitely not Not sure / it depends",
GENFBACK_no_prevent_all="Genetic feedback for conditions that ARE NOT prevetable or treatable (e.g. some types of dementia)?
Levels: Yes = Yes definitely Yes probably; No =  No, probably not No, definitely not; Unsure = Not sure / it depends",
GENFBACK_ancestry_agree="Genetic feedback for ancestry?
Levels: Yes = Yes definitely Yes probably; No =  No, probably not No, definitely not Not sure / it depends",
GENFBACK_ancestry_all="Genetic feedback for ancestry?
Levels: Yes = Yes definitely Yes probably; No =  No, probably not No, definitely not; Unsure = Not sure / it depends",
OFHBEN_1="OFH will... advance medical research"
,OFHBEN_2="OFH will... better treatments"
,OFHBEN_3="OFH will... early detection"
,OFHBEN_4="OFH will... help me"
,OFHBEN_5="OFH will... help family/friends"
,OFHBEN_6="OFH will... help community"
,OFHBEN_7="OFH will... help people in UK"
,OFHBEN_8="OFH will... help people in world"
,OFHBEN_9="OFH will... help representation of people like me"
,BARRSA_1="Comfortable health info in large database"
,BARRSA_2="Comfortable share health info with OFH"
,BARRSA_3="Comfortable how OFH use health info"
,BARRSA_4="Comfortable OFH access to medical records"
,BARRSB_1="Comfortable academics access to health records"
,BARRSB_2="Comfortable companies access to health records"
,BLOODS_1="Willing give sample if part of routine blood test"
,BLOODS_2="Willing give sample if soley for OFH"
,BLOODS_3="Difficult to give sample on weekday"
,BLOODS_4="Difficult to give sample on weekend"
,PRACBAR_2="have time for 10 min questionnaire"
,PRACBAR_3="have time for 30 min questionnaire")

```

Fix  value label of religiosity variable  for clarity. First print old values and tale to make sure this works as intended.

```{r print old vals and tables}

levels(factor_df$RELIGIOSITY)
table(factor_df$RELIGIOSITY)

```

```{r fix value labels}

levels(factor_df$RELIGIOSITY) <- c("Missing reponse","Practising","Not practising","Not religious") 
levels(factor_df$MARSTAT) <- c("Missing reponse","Married/civil partnership","Neither","Prefer not to say") 
  
```

check this worked as expected

```{r print new vals and tables}

levels(factor_df$RELIGIOSITY)
table(factor_df$RELIGIOSITY)

```

## Transform to numeric where appropriate

The trust variables are currently unordered factors, but should be numeric (how much do you trust.... on a scale of 0 - 10)


```{r transform trust to numeric}

factor_df <- factor_df %>%
  mutate(across(starts_with("TRUST"), 
         ~as.numeric(case_when(. == "0 - Do not trust at all" ~ 0,
                               . == "10 - Trust completely" ~ 10,
                               . == "1" ~ 1,
                               . == "2" ~ 2,
                               . == "3" ~ 3,
                               . == "4" ~ 4,
                               . == "5" ~ 5,
                               . == "6" ~ 6,
                               . == "7" ~ 7,
                               . == "8" ~ 8,
                               . == "9" ~ 9,
                               TRUE ~ NA_real_ ))))

```

Check this worked as expected

```{r show trust variables}

factor_df %>% 
  select(starts_with("TRUST")) %>%
  skim() %>%
  select(skim_type, skim_variable, n_missing, numeric.mean, numeric.sd,numeric.hist)

table(factor_df$TRUSTGEN)
```

## create summed variables 

This will include
* A summed variable summarising ease of use of internet for life admin (DIGPROF vars)
* A summed variable summarising volunteering (PROSO vars)
* A summed variable summarising research participation (sci vars??)
* A summed variable summarising trust in science


### Create vectors for the summary score items

#### Digital proficiency 

**Digital proficiency scoring**

Dont know = 0
Not at all confident = 0
Not very confident = 1
Fairly confident = 2
Very confident = 3

minimum score = 0 (not at all confident on any)
maximum score = 15 (very confident for all)

```{r sum score vectors digi proficiency}

# Digital proficiency
Digprof_cols <- factor_df %>%
  select(contains("DIGPROF")) %>%
  colnames() 

lapply(factor_df[Digprof_cols],label) 

```
    
#### Any lifetime pro social

```{r sum score vectors prosocial ever}
# Volunteering ever
Volunteering.ever_cols <- factor_df %>%
  select(contains("PROSO_"),
         -"PROSO_NONE") %>%
  colnames()

lapply(factor_df[Volunteering.ever_cols],label)

```

####  4 weeks pro social
```{r sum score vectors prosocial 4 weeks}
# Volunteering ever
Volunteering.4_cols <- factor_df %>%
  select(contains("PROSO4W_"),
         -"PROSO4W_NONE") %>%
  colnames()

lapply(factor_df[Volunteering.4_cols],label)

```

#### Scientific trust
```{r sum score vectors science}
# Volunteering 4 weeks
science_cols <- factor_df %>%
  select(contains("SCI"),
         -c("SCIINF","SCIINT")) %>%
  colnames()

lapply(factor_df[science_cols],label)

```

#### research participation

```{r sum score vectors research participation}
# Volunteering 4 weeks
participation_cols <- factor_df %>%
  select(contains("HRES"),
         -c("HRES_NONE","HRES_DK")) %>%
  colnames()

lapply(factor_df[participation_cols],label)

```

### create sum scores.

use column vectors to mutate new columns

#### Digital proficiency 

**Digital proficiency scoring**

Dont know = 0
Not at all confident = 0
Not very confident = 1
Fairly confident = 2
Very confident = 3

minimum score = 0 (not at all confident on any)
maximum score = 15 (very confident for all)

```{r create digital proficiency sum score}

 factor_df <- factor_df %>%
  mutate(DIGPROF_TOTAL = 0 + rowSums(factor_df[Digprof_cols] == "Not very confident") + 
           (rowSums(factor_df[Digprof_cols] == "Fairly confident")*2) +
           (rowSums(factor_df[Digprof_cols] == "Very confident")*3)) 


factor_df = apply_labels(factor_df, 
DIGPROF_TOTAL="Composite score indicating overall ease of use of internet for life admin. Minimum 0 indicating not at all confident and maximum of 15 indicating very confident")
```

#### Pro social 
**Pro social (Ever) and pro social 4 weeks**

Yes = 1
No = 0 

minimum score = 0 (no volunteering ever)
Maximum score = 3 (donated blood, donated money to charity, volunteered EVER)

```{r create prosocial sum scores}

 factor_df <- factor_df %>%
  mutate(PROSO_EVER_TOTAL = 0 + rowSums(factor_df[Volunteering.ever_cols] == "Yes"),
         PROSO4W_TOTAL = 0 + rowSums(factor_df[Volunteering.4_cols] == "Yes"),
         ) 


factor_df = apply_labels(factor_df, 
PROSO_EVER_TOTAL="Composite score indicating number of pro social activities ever undertaken. Minimum score of 0 indicates none of the three were endorsed, maximum of 3 indicates all activities endorsed",
PROSO4W_TOTAL="Composite score indicating number of pro social activities undertaken in the past 4 weeks. Minimum score of 0 indicates none of the three were endorsed, maximum of 3 indicates all activities endorsed")
```

#### Trust in science 

Strongly agree = 2
Agree = 1
Neither agree nor disagree = 0
Disagree -1
Strongly disagree = -2
Don't know = 0

minimum score = -6 (strong distrust of science)
maximum score = 6 (Strong trust in science)
Score of 0 indicates neutrality

```{r create trust in science  sum score}

 factor_df <- factor_df %>%
  mutate(SCITRUST_TOTAL = 0 + (rowSums(factor_df[science_cols] == "Strongly agree") * 2) +
         (rowSums(factor_df[science_cols] == "Agree")) +
         (rowSums(factor_df[science_cols] == "Disagree") * -1) +
         (rowSums(factor_df[science_cols] == "Strongly disagree") * -2)
         ) 


factor_df = apply_labels(factor_df, 
SCITRUST_TOTAL="Composite score indicating trust or distrust in science overall. A negative score indicates greater distrust overall and a positive score indicates greater trust overall.")
```

#### Research participation


Yes = 1
No = 0 

minimum score = 0 (never taken part in health research)
Maximum score = 3 (taken part in clinical trials, focus groups and surveys)

```{r create research participation sum score}

 factor_df <- factor_df %>%
  mutate(HRES_TOTAL = 0 + (rowSums(factor_df[participation_cols] == "YES"))
         ) 


factor_df = apply_labels(factor_df, 
HRES_TOTAL="Summed score indicating research participation. Minimum value of 0 indicates no previous participation in research, maximum value of 3 indicates previous participation in survey, clinical trials and focus groups.")
```


# Data preparation

prepare lists of variables that we are interested in for data summaries,
and additional lists for predictors and outcomes we want to test in univariable regressions


***All variables***
Note, using total score variables instead of individual variables where composites or sum scores exist
```{r list of vars for univariable analyses}
all.vars <- c(
"Black_filter", "Asian_filter", "MDQuintile", "AGE", "AGE_BAND", 
"SEX", "ETHNICITY", "ETHNICITY_LFS", "NUMPEOPLE", "NUMADULTS", 
"NUMCHILDU16", "COHAB", "COHAB_BINARY", "MARSTAT", "CHILDHERE", 
"NumOwnChildrenU16HH", "OwnChildU16OutsideHH", "HHSTRUCTURE", 
"PLACEINHH", "INTERNET", "DEVICE_SMRTPHNE", "DEVICE_MOBILE", 
"DEVICE_LANDLINE", "DEVICE_TABLET", "DEVICE_CPU", "DEVICE_SMRTTV", 
"DEVICE_GAME", "DEVICE_STREAM", "DEVICE_WEAR", "DEVICE_TOTAL", 
"DIGPROF_TOTAL", "FINNOW", "RELIGIOSITY", "RELIGION", "QUALTYPE", 
"EDUCATION", "DEGREE", "WorkingStatus_PrePandemic", "WorkingStatus_PrePandemic_Binary", 
"WorkingStatus", "WorkingStatus_Binary", "OCCUPATION_SOC2010", 
"OCCUPATION_NSSEC", "TENURE", "LIFEEVENT", "PROSO_EVER_TOTAL", 
"PROSO4W_TOTAL","DISABILITY", 
"DISAB1", "DISAB2", "DISABEVER", "GENFAM", "GENTEST", "GENTEST_1", 
"GENTEST_2", "GENTEST_3", "GENTEST_4", "GENTEST_5", "GENTEST_5OPEN", 
"GENTTYP_1", "GENTTYP_2", "GENTTYP_3", "GENTTYP_4", "GENTTYP_5", 
"DISABFAM", "AID", "HEALTH", "HRES_TOTAL","HACT12_1", "HACT12_2", 
"HACT12_3", "HACT12_4", 
"TRUSTGEN", "TRUSTORG_A", "TRUSTORG_B", "TRUSTORG_C", "TRUSTORG_D", 
"TRUSTORG_E", "SCIINT", "SCIINF", "SCITRUST_TOTAL",
"COVRES", "OFHAWARE", "VIDEO", "AUDIO", "UNDERST", "OFHACT", 
"OFHYN_FREQ", "OFHYN_OPEN", "OFHDK_FREQ", "OFHDK_OPEN", "OFHDK2_FREQ", 
"OFHDK2_OPEN", "OFHPAIR_A", "OFHPAIR_B", "OFHPAIR_C", "OFHPAIR_D", 
"OFHPAIR_E", "OFHBEN_1", "OFHBEN_2", "OFHBEN_3", "OFHBEN_4", 
"OFHBEN_5", "OFHBEN_6", "OFHBEN_7", "OFHBEN_8", "OFHBEN_9", "OFHBENCL", 
"BARRSA_1", "BARRSA_2", "BARRSA_3", "BARRSA_4", "BARRSB_1", "BARRSB_2", 
"BLOODS_1", "BLOODS_2", "BLOODS_3", "BLOODS_4", "BLOODS_5", "BLOODS_6", 
"BLOODS_7", "PRACBAR_1", "PRACBAR_2", "PRACBAR_3", "GENFBACK_1", 
"GENFBACK_2", "GENFBACK_3", "PARTNA", "PARTNB", "OFHACT2", "RECONTACT", 
"ofhact_agree", "ofhact_all", "ofhact_unsure", "GENFBACK_prevent_agree", 
"GENFBACK_prevent_all", "GENFBACK_no_prevent_agree", "GENFBACK_no_prevent_all", 
"GENFBACK_ancestry_agree", "GENFBACK_ancestry_all")
```

***demographic characteristics***
```{r list of demographic vars for univariable analyses}
dem.vars <- c(
"Black_filter", "Asian_filter", "MDQuintile", "AGE_BAND", 
"SEX", "ETHNICITY", "ETHNICITY_LFS", "NUMPEOPLE", "MARSTAT", 
"NumOwnChildrenU16HH", "OwnChildU16OutsideHH", "RELIGIOSITY", "RELIGION", "QUALTYPE", 
"EDUCATION", "DEGREE", "WorkingStatus_PrePandemic", "WorkingStatus_PrePandemic_Binary", 
"WorkingStatus", "WorkingStatus_Binary", "OCCUPATION_SOC2010", 
"OCCUPATION_NSSEC", "TENURE",  "DISABILITY", 
"DISAB1", "DISAB2", "DISABEVER")
```

***outcomes***
```{r list of outcome vars for univariable analyses}
primary.outcome.binary <- "ofhact_agree" # intention to participate
primary.outcome.all <- "ofhact_all" #intention to participate, including unsure

gen.outcome.preventable.binary <- "GENFBACK_prevent_agree"
gen.outcome.preventable.all <- "GENFBACK_prevent_all"

gen.outcome.nonpreventable.binary <- "GENFBACK_no_prevent_agree"
gen.outcome.nonpreventable.all <- "GENFBACK_no_prevent_all"

gen.outcome.ancestry.binary <- "GENFBACK_ancestry_agree"
gen.outcome.ancestry.all <- "GENFBACK_ancestry_all"

outcomes <- c("ofhact_agree","ofhact_all",
              "GENFBACK_prevent_agree","GENFBACK_prevent_all",
                  "GENFBACK_no_prevent_agree","GENFBACK_no_prevent_all",
                  "GENFBACK_ancestry_agree","GENFBACK_ancestry_all")
  
```

***independent variables***
```{r list of independent vars for univariable analyses}
pred.participate.vars <- c(
"MDQuintile",  "AGE_BAND", 
"SEX", "ETHNICITY_LFS", "NUMPEOPLE",
"NumOwnChildrenU16HH", "OwnChildU16OutsideHH", "INTERNET", "DEVICE_SMRTPHNE", "DEVICE_MOBILE", 
 "DEVICE_TABLET", "DEVICE_CPU", "DEVICE_WEAR", "DEVICE_TOTAL", 
"DIGPROF_TOTAL", "FINNOW", "RELIGIOSITY", "RELIGION", 
"EDUCATION",  "WorkingStatus_Binary", "OCCUPATION_SOC2010", 
 "LIFEEVENT", "PROSO_EVER_TOTAL","PROSO4W_TOTAL", 
"GENFAM", "GENTEST",
"DISABFAM", "AID", "HEALTH", "HRES_TOTAL",
"HACT12_1", "HACT12_2", "HACT12_3", "HACT12_4", 
"TRUSTGEN", "TRUSTORG_A", "TRUSTORG_B", "TRUSTORG_C", "TRUSTORG_D", 
"TRUSTORG_E", "SCIINT", "SCIINF", "SCITRUST_TOTAL", 
"COVRES", "OFHAWARE", "UNDERST", "OFHACT", 
"OFHYN_FREQ", "OFHYN_OPEN", "OFHDK_FREQ", "OFHDK_OPEN", "OFHDK2_FREQ", 
"OFHDK2_OPEN", "OFHPAIR_A", "OFHPAIR_B", "OFHPAIR_C", "OFHPAIR_D", 
"OFHPAIR_E", "OFHBEN_1", "OFHBEN_2", "OFHBEN_3", "OFHBEN_4", 
"OFHBEN_5", "OFHBEN_6", "OFHBEN_7", "OFHBEN_8", "OFHBEN_9", "OFHBENCL", 
"BARRSA_1", "BARRSA_2", "BARRSA_3", "BARRSA_4", "BARRSB_1", "BARRSB_2", 
"BLOODS_1", "BLOODS_2", "BLOODS_3", "BLOODS_4", "BLOODS_5", "BLOODS_6", 
"BLOODS_7", "PRACBAR_1", "PRACBAR_2", "PRACBAR_3", "GENFBACK_1", 
"GENFBACK_2", "GENFBACK_3", "PARTNA", "PARTNB", "OFHACT2", "RECONTACT", 
 "GENFBACK_prevent_agree", 
"GENFBACK_prevent_all", "GENFBACK_no_prevent_agree", "GENFBACK_no_prevent_all", 
"GENFBACK_ancestry_agree", "GENFBACK_ancestry_all")


  
pred.gen.vars <-c(
"MDQuintile",  "AGE_BAND", 
"SEX", "ETHNICITY_LFS", "NUMPEOPLE",
"NumOwnChildrenU16HH", "OwnChildU16OutsideHH", "INTERNET", "DEVICE_SMRTPHNE", "DEVICE_MOBILE", 
 "DEVICE_TABLET", "DEVICE_CPU", "DEVICE_WEAR", "DEVICE_TOTAL", 
"DIGPROF_TOTAL", "FINNOW", "RELIGIOSITY", "RELIGION", 
"EDUCATION",  "WorkingStatus_Binary", "OCCUPATION_SOC2010", 
 "LIFEEVENT", "PROSO_EVER_TOTAL","PROSO4W_TOTAL",  "GENFAM", "GENTEST", 
"DISABFAM", "AID", "HEALTH", "HRES_TOTAL","HACT12_1", "HACT12_2", "HACT12_3", "HACT12_4", 
"TRUSTGEN", "TRUSTORG_A", "TRUSTORG_B", "TRUSTORG_C", "TRUSTORG_D", 
"TRUSTORG_E", "SCIINT", "SCIINF", "SCITRUST_TOTAL", 
"COVRES", "OFHAWARE", "UNDERST", "OFHACT", 
"OFHYN_FREQ", "OFHYN_OPEN", "OFHDK_FREQ", "OFHDK_OPEN", "OFHDK2_FREQ", 
"OFHDK2_OPEN", "OFHPAIR_A", "OFHPAIR_B", "OFHPAIR_C", "OFHPAIR_D", 
"OFHPAIR_E", "OFHBEN_1", "OFHBEN_2", "OFHBEN_3", "OFHBEN_4", 
"OFHBEN_5", "OFHBEN_6", "OFHBEN_7", "OFHBEN_8", "OFHBEN_9", "OFHBENCL", 
"BARRSA_1", "BARRSA_2", "BARRSA_3", "BARRSA_4", "BARRSB_1", "BARRSB_2", 
"BLOODS_1", "BLOODS_2", "BLOODS_3", "BLOODS_4", "BLOODS_5", "BLOODS_6", 
"BLOODS_7", "PRACBAR_1", "PRACBAR_2", "PRACBAR_3",  
"PARTNA", "PARTNB", "OFHACT2", "RECONTACT","ofhact_agree", "ofhact_all", "ofhact_unsure")

all.pred.vars <- c(
"MDQuintile",  "AGE_BAND", 
"SEX", "ETHNICITY_LFS", "NUMPEOPLE",
"NumOwnChildrenU16HH", "OwnChildU16OutsideHH", "INTERNET", "DEVICE_SMRTPHNE", "DEVICE_MOBILE", 
 "DEVICE_TABLET", "DEVICE_CPU", "DEVICE_WEAR", "DEVICE_TOTAL", 
"DIGPROF_TOTAL", "FINNOW", "RELIGIOSITY", "RELIGION", 
"EDUCATION",  "WorkingStatus_Binary", "OCCUPATION_SOC2010", 
 "LIFEEVENT", "PROSO_EVER_TOTAL","PROSO4W_TOTAL", "GENFAM", "GENTEST",  
"DISABFAM", "AID", "HEALTH", "HRES_TOTAL","HACT12_1", "HACT12_2", "HACT12_3", "HACT12_4", 
"TRUSTGEN", "TRUSTORG_A", "TRUSTORG_B", "TRUSTORG_C", "TRUSTORG_D", 
"TRUSTORG_E", "SCIINT", "SCIINF", "SCITRUST_TOTAL", 
"COVRES", "OFHAWARE", "UNDERST", "OFHACT", 
 "OFHPAIR_A", "OFHPAIR_B", "OFHPAIR_C", "OFHPAIR_D", 
"OFHPAIR_E", "OFHBEN_1", "OFHBEN_2", "OFHBEN_3", "OFHBEN_4", 
"OFHBEN_5", "OFHBEN_6", "OFHBEN_7", "OFHBEN_8", "OFHBEN_9", "OFHBENCL", 
"BARRSA_1", "BARRSA_2", "BARRSA_3", "BARRSA_4", "BARRSB_1", "BARRSB_2", 
"BLOODS_1", "BLOODS_2", "BLOODS_3", "BLOODS_4", "BLOODS_5", "BLOODS_6", 
"BLOODS_7", "PRACBAR_1", "PRACBAR_2", "PRACBAR_3",  
"PARTNA", "PARTNB", "OFHACT2", "RECONTACT")

gated.pred.vars <- c("GENTEST_1", 
"GENTEST_2", "GENTEST_3", "GENTEST_4", "GENTEST_5", "GENTEST_5OPEN", 
"GENTTYP_1", "GENTTYP_2", "GENTTYP_3", "GENTTYP_4", "GENTTYP_5",
"OFHYN_FREQ", "OFHYN_OPEN", "OFHDK_FREQ", "OFHDK_OPEN", "OFHDK2_FREQ", 
"OFHDK2_OPEN",)
```
##### DOING/To DO
finish cutting gated vars out of the variable lists
create an aggreagte score for seeking information about different things 

# Data summaries {.tabset}
Summarise and plot raw data

## Frequency tables
### demographic variables
```{r tabular descriptions of demographic variables, eval=F}

summarytools::dfSummary(
  factor_df[dem.vars],
  graph.col = F,
  valid.col = F,
  labels.col = T)

```
### outcome variables
```{r tabular descriptions of outcome variables, eval=F}

summarytools::dfSummary(
  factor_df[outcomes],
  graph.col = F,
  valid.col = F,
  labels.col = T)

```
### predictor variables
```{r tabular descriptions of outcome variables, eval=F}

summarytools::dfSummary(
  factor_df[all.pred.vars],
  graph.col = F,
  valid.col = F,
  labels.col = T)

```

## Histograms
### demographic variables

 

# Analyses
## recode variables

recode dont know, prefer not to say and and missing response as NA (missing data) in the analytic data set. 

Retain dont know and prefer not to say in factor df for summaries. 

Capture a list of variable labels as these get lost in the NA process

```{r capture labels, results='hide'}
label_list <- dput(sapply(factor_df,label))
```

first remove missing data and set to NA in the factor dataset

```{r set missing data to NA}


factor_df <- factor_df %>%
  mutate(across(where(is.factor), 
                ~as.factor(case_when(. =="Missing reponse" ~ NA_character_, 
                                     TRUE ~ as.character(.)))))
  
```



then change all (dont know, prefer not to say, missing) to NA for the analytic data set

```{r set all non responses to NA}

regression_df <- factor_df %>%
  mutate(across(where(is.factor), 
                ~as.factor(case_when(. =="Don't know" ~ NA_character_,
                                     . =="Prefer not to say" ~ NA_character_,
                                     TRUE ~ as.character(.)))))
```

add labels back to data set

```{r add labels to factor df}

label(factor_df) = as.list(label_list[match(names(factor_df), names(label_list))])
label(regression_df) = as.list(label_list[match(names(regression_df), names(label_list))])

```


## univariable regressions 
Replicate Alice's regressions. identify which demographic features are important to use as covariates in multivariable regressions. 

(note, will use multinomial regression for the three outcome variables where we predict unsure alongside yes and no)


## multivariable regressions

